Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-07 manuscript.tex
7 updates

We also present in this paper a new function to correct for stellar activity signals. Generally, when fitting for planetary signals, people use a model composed of one or several Keplerians to account for the planets, in addition to a linear combination with the FWHM and BIS SPAN of the CCF to account for stellar activity signals. The new function proposes to add a linear dependency with the amplitude of the CCF retrieved either by the SN or Normal density fit, and an interaction term between the asymmetry and the width parameters. On the simulated data from SOAP 2.0, this new model allows to mitigate stellar activity signals by a factor of 2 and 3.5 better compared to the model generally used, for the faculae and spot, respectively.

>>>>

We also propose a new model to correct estimated RV data for stellar activity signals. 
Generally, when fitting for planetary signals, it is common to use a model composed of one or several Keplerian signals to account for the planets, in addition to a linear combination of the FWHM and BIS SPAN to account for stellar activity signals. 
The proposed model adds an additional term to account for the amplitude of the CCF, and an interaction term between the estimated asymmetry and the width parameters. 
Using the simulated data from SOAP 2.0, this new model reduces the effect of the stellar activity signal by a factor of 2 and 3.5 over the usual model, for the facula and spot, respectively.
